Augmentation of a Historical Harpsichord Keyboard Replica for Haptic-Enabled Interaction in Museum Exhibitions

### 2025-01-27 src/main.tex
Updates from Overleaf

%% Version 1
This paper describes the design and creation of an electronically augmented replica of a 16th-century harpsichord keyboard with a typical Renaissance Italian layout to create a digital musical instrument. % [1]
The keyboard was commissioned for exhibition in a musical instrument museum as an enhancement to the visitor experience by providing an interface to digitised versions of instruments within the collection. % [2]
This project also addresses how we can interact with digitally conserve historic musical instruments when the interface is a limiting factor to the verisimilitude of the experience. % [2,3]
This ultimately culminated in a design for an interface capable of new expressions by extending, rather than forfeiting, the characteristics of the original. % [4]

The tactile feedback of the keyboard is created by incorporating the same mechanics as a single manual two-register harpsichord with strings under tension in order to replicate the mechanical resistance characteristic of the original compass. % [1]
An array of optical sensors connected to a microcontroller was installed within the interface to generate continuous streams of data corresponding to the vertical motion of each jack. % [1, ~4]
We outline the details of the keyboard's design principles, technical development, and the motivations behind them. % [1]

@@

% This project embodies the entanglement between musical instrument cultural heritage and its relationship with new and increasing accessible technologies. [3, 4]
% Acknowledgment and conscientiousness to older designs and aesthetics have been used in service of, rather than obstruction to, richer interactions with digital musical instruments.[2,3,4]
% This ultimately culminated in a design for an interface capable of new expressions by extending, rather than forfeiting, the characteristics of the original. % [4]
% We outline the details of the keyboard's design principles, technical development, and the motivations behind them. % [1]

>>>>

%% Version 1
This paper describes the design and creation of an electronically augmented replica of a 16th-century harpsichord keyboard with a typical Renaissance Italian layout to create a vibrotactile digital musical instrument. % [1]
The tactile feedback of the keyboard is created by incorporating the same mechanics as a single manual two-register harpsichord with strings under tension in order to replicate the mechanical resistance characteristic of the original compass. % [1]
An array of optical sensors connected to a microcontroller was installed within the interface to generate continuous streams of data corresponding to the vertical motion of each jack. % [1, ~4]

The keyboard was commissioned for exhibition in a musical instrument museum as an enhancement to the visitor experience by providing an interface to digitised versions of instruments within the collection. % [2]
This project also addresses how we can interact with digitally conserved historic musical instruments when the interface is a limiting factor to the verisimilitude of the experience. % [2,3]
This ultimately culminated in a design for an interface capable of new expressions by extending, rather than forfeiting, the characteristics of the original. % [4]
We outline the details of the keyboard's design principles, technical development, and the motivations behind them. % [1]

@@

% This project embodies the entanglement between musical instrument cultural heritage and its relationship with new and increasingly accessible technologies.% [3, 4]
% Acknowledgment and conscientiousness of older designs and aesthetics have been used in service of, rather than obstruction to, richer interactions with digital musical instruments.%[2,3,4]
%  This ultimately culminated in a design for an interface capable of new expressions by extending, rather than forfeiting, the characteristics of the original. % [4]
% We outline the details of the keyboard's design principles, technical development, and the motivations behind them. % [1]
